Kernel Phase and Coronagraphy with Automatic Differentiation

### 2020-05-18 ms.tex
Updates from Overleaf

We then use Markov Chain Monte Carlo \citep{metropolis53} to sample from the posterior assuming Gaussian likelihoods, using the \texttt{emcee} affine-invariant ensemble sampler \citep{emcee}. We obtain binary parameters of separation $\rho = 115.3 \pm 1.1$~mas, position angle $\theta = 85.7 \pm 0.25$~degrees, and contrast $c = 25.4 \pm 0.5$: these are close to the \citet{martinache20} figures, but differ by much more than their small uncertainties. For comparison, the contrast ratio of the system is expected from resolved imaging to be $28.0 \pm 8.3$ in $K$-band \citep{hinkley11}.

@@

>>>>

We then use Markov Chain Monte Carlo \citep{metropolis53} to sample from the posterior assuming Gaussian likelihoods, using the \texttt{emcee} affine-invariant ensemble sampler \citep{emcee}. We obtain binary parameters of separation $\rho = 115.3 \pm 1.2$~mas, position angle $\theta = 85.6 \pm 0.27$~degrees, and contrast $c = 26.3 \pm 0.6$: these are close to the \citet{martinache20} figures, but differ by much more than their small uncertainties. For comparison, the contrast ratio of the system is expected from resolved imaging to be $28.0 \pm 8.3$ in $K$-band \citep{hinkley11}.

@@

In order to investigate this discrepancy, we generated a grid of forwards models
